---
title: "Final Project"
author: "Maximilian Rychwalski"
date: "5/1/2020"
output: html_document
---

### United Nations

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(plotly)
library(DT)
```

```{r}
dfpop = read.csv("WPP2019_TotalPopulationBySex.csv")
```

### Population development in Syria (Medium vs. zero-migration)
```{r}
dfpop_syria <- dfpop %>%
  filter(Variant %in% c("Medium", "Zero migration")) %>%
  filter(Location == "Syrian Arab Republic")
plot_popsyria <- ggplot(data=dfpop_syria, aes(x=Time, y=PopTotal, fill=Variant, color=Variant)) + geom_line()
plot_popsyria
```

### Population development in South Sudan (Medium vs. zero-migration)
```{r}
dfpop_sudan <- dfpop %>%
  filter(Variant %in% c("Medium", "Zero migration")) %>%
  filter(Location == "South Sudan")
plot_popsudan <- ggplot(data=dfpop_sudan, aes(x=Time, y=PopTotal, fill=Variant, color=Variant)) + geom_line()
plot_popsudan
```

### Population development in Venezuela (Medium vs. zero-migration)
```{r}
dfpop_venezuela <- dfpop %>%
  filter(Variant %in% c("Medium", "Zero migration")) %>%
  filter(Location == "Venezuela (Bolivarian Republic of)")
plot_popvenezuela <- ggplot(data=dfpop_venezuela, aes(x=Time, y=PopTotal, fill=Variant, color=Variant)) + geom_line()
plot_popvenezuela
```


### Period Indicatiors (Medium)
```{r}
dfperiod_medium = read.csv("WPP2019_Period_Indicators_Medium.csv")
dfm_countries <- dfperiod_medium %>%
  filter(Location %in% c("Syrian Arab Republic", "Venezuela (Bolivarian Republic of)", "South Sudan"))
```

### Period Indicatiors (Zero Migration)
```{r}
dfperiod_zm = read.csv("WPP2019_Period_Indicators_OtherVariants.csv")
dfzm_countries <- dfperiod_zm %>%
  filter (Variant == "Zero migration") %>%
  filter(Location %in% c("Syrian Arab Republic", "Venezuela (Bolivarian Republic of)", "South Sudan"))
```

### Total fertility in live births per woman (Medium)
```{r}
plot_tfrmcountries <- ggplot(data=dfm_countries, aes(x=MidPeriod, y=TFR, fill=Location, color=Location)) + geom_line()
plot_tfrmcountries
```

### Total fertility in live births per woman (Zero migration)
```{r}
plot_tfrzmcountries <- ggplot(data=dfzm_countries, aes(x=MidPeriod, y=TFR, fill=Location, color=Location)) + geom_line()
plot_tfrzmcountries
```

### Births in number of births including both sexes combined in thousands (Medium)
```{r}
plot_birthsmcountries <- ggplot(data=dfm_countries, aes(x=MidPeriod, y=Births, fill=Location, color=Location)) + geom_line()
plot_birthsmcountries
```

### Births in number of births including both sexes combined in thousands (Zero migration)
```{r}
plot_birthszmcountries <- ggplot(data=dfzm_countries, aes(x=MidPeriod, y=Births, fill=Location, color=Location)) + geom_line()
plot_birthszmcountries
```

### Deaths in number of births including both sexes combined in thousands (Medium)
```{r}
plot_deathsmcountries <- ggplot(data=dfm_countries, aes(x=MidPeriod, y=Deaths, fill=Location, color=Location)) + geom_line()
plot_deathsmcountries
```

### Deaths in number of births including both sexes combined in thousands (Zero migration)
```{r}
plot_deathszmcountries <- ggplot(data=dfzm_countries, aes(x=MidPeriod, y=Deaths, fill=Location, color=Location)) + geom_line()
plot_deathszmcountries
```
