---
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

# Load packages.
packages <- c("ggplot2", "tidyverse", "wbstats", "leaflet","rgdal","countrycode")

packages <- lapply(packages, FUN = function(x) {
  if(!require(x, character.only = TRUE)) {
    install.packages(x, repos = "http://cran.us.r-project.org")
    library(x, character.only = TRUE)
  }
})
```


# Migration Case Study: Analysis of Top 3 Migration Outflows {.tabset .tabset-fade}

## Introduction {.tabset .tabset-fade .tabset-pills}

### 2017 World Migration Flows

```{r, message=FALSE, }
myspdf = readOGR(dsn= "data",layer="TM_WORLD_BORDERS_SIMPL-0.3", verbose = FALSE)
df <- wb(country = "countries_only",indicator = c("SM.POP.NETM","SP.POP.TOTL"),  
         startdate = 2017, enddate = 2017)

df <- df %>%
  dplyr::left_join(wbstats::wbcountries() %>%                         
                     dplyr::select(iso3c, region)) %>%
  tidyr::pivot_wider(
    id_cols = c("date","iso3c", "country", "region"), 
    names_from = indicator, 
    values_from = value
    )

#calculate per 1,000 rate and define categories based on zero threshold
df <- mutate(df,'Per 1,000 Rate' =(df$`Net migration` / df$`Population, total`)*1000)

#round rate to two decimal places
df$`Per 1,000 Rate` <- round(df$`Per 1,000 Rate`, digits = 1) 

#categorizes flows of migration
df <- mutate(df, 
             Type = case_when(
               `Per 1,000 Rate` > 0  ~ "Inflow",
               `Per 1,000 Rate` < 0  ~ "Outflow",
               TRUE                  ~  "Data Not Avalilable"
    )
  )

format_num = function(n){
  case_when(
    abs(n) >= 1e12 ~ paste(round(n/1e12), 'Tn'),
    abs(n) >= 1e9 ~ paste(round(n/1e9), 'Bn'),
    abs(n) >= 1e6 ~ paste(round(n/1e6), 'M'),
    abs(n) >= 1e3 ~ paste(round(n/1e3), 'K'),
    TRUE ~ as.character(n))
}
df$`Net migration` <- format_num(df$`Net migration`)
df$`Population, total` <- format_num(df$`Population, total`)

#adds merged data into spdf
df$iso3c <- countrycode(df$iso3c, "iso3c", "iso3c", nomatch = NULL)
myspdf$ISO3 <- countrycode(myspdf$ISO3, "iso3c","iso3c", nomatch = NULL)
combined <- myspdf@data %>% 
  left_join(df, by = c("ISO3" = "iso3c"))
myspdf@data <- combined

#coloring of palattes
combined_outflow <- filter(combined,combined$Type=="Outflow")
qpal_outflow <- colorBin("Reds",combined_outflow$`Per 1,000 Rate`, bins=4,reverse = TRUE)

combined_inflow <- filter(combined,combined$Type=="Inflow")
qpal_inflow <- colorBin("Greens",combined_inflow$`Per 1,000 Rate`,bins = c(2,4,8,16,32,160))

#popup content
content <- paste("<strong>Country:</strong>",myspdf$NAME,"<br/>",
                 "<strong>Net Migration:</strong>",myspdf$`Net migration`,"<br/>",
                 "<strong>Population:</strong>",myspdf$`Population, total`,"<br/>",
                 "<strong>Rate Per 1000:</strong>", myspdf$`Per 1,000 Rate`,"People","<br/>")
```

```{r, warning=FALSE,message=FALSE, fig.align="center"}
leaflet(myspdf,options = leafletOptions(zoomControl = TRUE, minZoom = 0, maxZoom = 4)) %>%
  addProviderTiles(providers$CartoDB.PositronNoLabels) %>%
  fitBounds(~-100,-50,~80,80) %>%
  setView(lat = 10, lng=0, zoom = 1) %>%
 #add fill for default
  addPolygons(stroke = TRUE, smoothFactor = 0.5,
              weight=1, color='#333333', opacity=1, popup = content) %>%
 #add fill for outflow
  addPolygons(group = "Outflow",stroke = TRUE, smoothFactor = 0.5,
              weight=1, color='#333333', opacity=1, popup = content, 
              fillColor = ~qpal_outflow(`Per 1,000 Rate`)) %>%
 #add legend for outflow
  addLegend(group = "Outflow",values = combined_outflow$`Per 1,000 Rate`,
            pal = qpal_outflow,
            title = "Migration Per 1000") %>%
 #add fill for inflow
  addPolygons(group = "Inflow",stroke = TRUE, smoothFactor = 0.5,
              weight=1, color='#333333', opacity=1, popup = content,
              fillColor = ~qpal_inflow(`Per 1,000 Rate`)) %>%
 #add legend for inflow
  addLegend(group = "Inflow",values = combined_inflow$`Per 1,000 Rate`,
            pal = qpal_inflow,
            title = "Migration Per 1000") %>%
 #control layer
  addLayersControl(overlayGroups = c("Outflow","Inflow"),  position = "bottomright",
                   options = layersControlOptions(collapsed = FALSE))
```

The World Bank Open Data set includes world development indicators that cover a wide range of metrics across the world. Using the `wb` package, we chose the migration (`SM.POP.NETM`) and population (`SP.POP.TOTL`) indicators to measure the flows of people in all areas were the data was available. The rate was computed using the typical convention of a person per 1000 people. This allows for ease of interpretation and comparability across countries. For example, a 4 rate would be interpreted as a 4 persons coming into the country per 1000 people of the current year's population. In a similar fasion, a -4 rate would be interpreted as 4 persons leaving the country per 1000 people.

The map shows the inflows (green) and outflows (red) migration patterns in 2017. The map shows an interesting pattern of the global south on average per country experiencing larger outflows than the global north. Focusing on the outflows, we see that venezuela and the Syrian Arab Republic having the highest rates at -125.2 and -111.1 persons per 1000 people respectively. Also, the other country that had the highest country but was not illustrated was south sudan which at the time of this data set was still part of Sudan.

In the next couple of sections we look closer at what migration patterns look like in these countries alongside sentiment of the media in towards these migrant outflows. 
