---
output: html_document
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE, prompt=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

# Load packages.
packages <- c("ggplot2", "tidyverse", "wbstats", "rgdal", "leaflet", "dplyr", "lubridate", "viridis","countrycode","ggthemes","stringi","tm","SnowballC","wordcloud","RColorBrewer","corpus","unikn", "purrr","gower","lme4","multcomp","mvtnorm","corpustools","reshape2", "leaflet.minicharts")

packages <- lapply(packages, FUN = function(x) {
  if(!require(x, character.only = TRUE)) {
    install.packages(x, repos = "http://cran.us.r-project.org")
    library(x, character.only = TRUE)
  }
})

# Removing scientific notation
options(scipen = 999)

theme_set(theme_clean())

```


# Migration Case Study: Analysis of Top 3 Countries by Migration Outflows {.tabset .tabset-fade}
### Project by Andres Montes Lopez, Richa Gupta, Samikshya Siwakoti, Maximilian Rychwalski

## Introduction {.tabset .tabset-fade .tabset-pills}

### 2017 World Migration Flows

```{r, message=FALSE }
myspdf = readOGR(dsn= "data",layer="TM_WORLD_BORDERS_SIMPL-0.3", verbose = FALSE)
df <- wb(country = "countries_only",indicator = c("SM.POP.NETM","SP.POP.TOTL"),  
         startdate = 2017, enddate = 2017)

df <- df %>%
  dplyr::left_join(wbstats::wbcountries() %>%                         
                     dplyr::select(iso3c, region)) %>%
  tidyr::pivot_wider(
    id_cols = c("date","iso3c", "country", "region"), 
    names_from = indicator, 
    values_from = value
    )

#calculate per 1,000 rate and define categories based on zero threshold
df <- mutate(df,'Per 1,000 Rate' =(df$`Net migration` / df$`Population, total`)*1000)

#round rate to two decimal places
df$`Per 1,000 Rate` <- round(df$`Per 1,000 Rate`, digits = 1) 

#categorizes flows of migration
df <- mutate(df, 
             Type = case_when(
               `Per 1,000 Rate` > 0  ~ "Inflow",
               `Per 1,000 Rate` < 0  ~ "Outflow",
               TRUE                  ~  "Data Not Avalilable"
    )
  )

format_num = function(n){
  case_when(
    abs(n) >= 1e12 ~ paste(round(n/1e12), 'Tn'),
    abs(n) >= 1e9 ~ paste(round(n/1e9), 'Bn'),
    abs(n) >= 1e6 ~ paste(round(n/1e6), 'M'),
    abs(n) >= 1e3 ~ paste(round(n/1e3), 'K'),
    TRUE ~ as.character(n))
}
df$`Net migration` <- format_num(df$`Net migration`)
df$`Population, total` <- format_num(df$`Population, total`)

#adds merged data into spdf
df$iso3c <- countrycode(df$iso3c, "iso3c", "iso3c", nomatch = NULL)
myspdf$ISO3 <- countrycode(myspdf$ISO3, "iso3c","iso3c", nomatch = NULL)
combined <- myspdf@data %>% 
  left_join(df, by = c("ISO3" = "iso3c"))
myspdf@data <- combined

#coloring of palattes
combined_outflow <- filter(combined,combined$Type=="Outflow")
qpal_outflow <- colorBin("Reds",combined_outflow$`Per 1,000 Rate`, bins=4,reverse = TRUE)

combined_inflow <- filter(combined,combined$Type=="Inflow")
qpal_inflow <- colorBin("Blues",combined_inflow$`Per 1,000 Rate`,bins = c(2,4,8,16,32,160))

#popup content
content <- paste("<strong>Country:</strong>",myspdf$NAME,"<br/>",
                 "<strong>Net Migration:</strong>",myspdf$`Net migration`,"<br/>",
                 "<strong>Population:</strong>",myspdf$`Population, total`,"<br/>",
                 "<strong>Rate Per 1000:</strong>", myspdf$`Per 1,000 Rate`,"People","<br/>")
```

```{r, warning=FALSE,message=FALSE, fig.align="center"}
leaflet(myspdf,options = leafletOptions(zoomControl = TRUE, minZoom = 0, maxZoom = 4)) %>%
  addProviderTiles(providers$MapBox) %>%
  fitBounds(~-100,-50,~80,80) %>%
  setView(lat = 10, lng=0, zoom = 1) %>%
 #add fill for default
  addPolygons(stroke = TRUE, smoothFactor = 0.5,
              weight=1, color='#333333', opacity=1, popup = content) %>%
 #add fill for outflow
  addPolygons(group = "Outflow",stroke = TRUE, smoothFactor = 0.5,
              weight=1, color='#333333', opacity=1, popup = content, 
              fillColor = ~qpal_outflow(`Per 1,000 Rate`)) %>%
 #add legend for outflow
  addLegend(group = "Outflow",values = combined_outflow$`Per 1,000 Rate`,
            pal = qpal_outflow,
            title = "Migration Per 1000") %>%
 #add fill for inflow
  addPolygons(group = "Inflow",stroke = TRUE, smoothFactor = 0.5,
              weight=1, color='#333333', opacity=1, popup = content,
              fillColor = ~qpal_inflow(`Per 1,000 Rate`)) %>%
 #add legend for inflow
  addLegend(group = "Inflow",values = combined_inflow$`Per 1,000 Rate`,
            pal = qpal_inflow,
            title = "Migration Per 1000") %>%
 #control layer
  addLayersControl(overlayGroups = c("Outflow","Inflow"),  position = "bottomright",
                   options = layersControlOptions(collapsed = FALSE))
```

### The world

```{r}
# SM.POP.NETM - World bank indicator for Net migration- total number of migrants
# SP.POP.TOTL - World bank indicator for Total population- total population
mig_pop <- wbstats::wb(country = "countries_only",indicator = c("SM.POP.NETM", "SP.POP.TOTL"),  startdate = "2007", enddate = "2020", return_wide = TRUE)

# Variable to calcualte migration per population
mig_pop$mig_by_pop <- mig_pop$SM.POP.NETM / mig_pop$SP.POP.TOTL

# Converting date to integer from string
mig_pop$date <- mig_pop$date %>% as.numeric()

# mig_pop %>%
#   ggplot(aes(x = date, y = mig_by_pop, color = country)) +
#   geom_point() +
#   geom_line(data = mig_pop[!is.na(mig_pop$mig_by_pop),], aes(group = country)) +
#   theme(legend.position = "none")

```

*The Beginning*

The number of international migrants in 2019 was estimated at 270 million. According to migrant data collected in 2017, one in every 30 people in this world is living outside of their country of birth.

Nearly two-thirds of the migrants are looking for work. But there have been massive displacements due to ongoing conflicts and violence. IOM’s Internal Displacement Monitoring Centre has said that a total of 41.3 million people were forced to flee their homes at the end of 2018 – a record since monitoring began in 1998.

We were interested in exploring more about this topic.

The most recent data in World Bank is available for the year 2017.

```{r}
# Extract top 3 and least 3 countries for labels
top3 <-  mig_pop %>%
  filter(date == 2017 & !is.na(mig_by_pop)) %>%
  arrange(desc(mig_by_pop)) %>%
  head(n = 3) %>%
  dplyr::select(country, mig_by_pop)

least4 <- mig_pop %>%
  filter(date == 2017 & !is.na(mig_by_pop)) %>%
  arrange(desc(mig_by_pop)) %>%
  tail(n = 4) %>%
  dplyr::select(country, mig_by_pop)

mig_pop %>%
  filter(date == 2017) %>%
  ggplot() +
  geom_bar(aes(y = mig_by_pop, x = country), stat = "identity", na.rm = TRUE) +
  xlab(NULL) + ylab("migration per person in the country") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  geom_text(data = top3, aes(x = country, y = mig_by_pop, label = country), color = "green", check_overlap = TRUE, vjust = 0, nudge_y = 0.01) +
  geom_text(data = least4, aes(x = country, y = mig_by_pop, label = country), color = "red", check_overlap = TRUE, vjust = 0, nudge_y = -0.01) +
  labs(
    title = "Migrants per capita (2017)",
    caption = "source: World Bank, Global Poverty Working Group.")
  
```

This graph shows that some countries stand out with higher than normal immigration like Bahrain, Maldives and Oman whereas some other countries are standing out because of all the people moving out of them. For example in Syria, for every 100 people in the country 12 people are moving to other countries.

We are interested in understanding what are the reasons that are making these people move out of their home countries.

We are removing Puerto Rico from our observations due to the fact that it is a part of United States and most of the migration that Puerto Rico faces is still inside of the country.

We are more interested in seeing the movement of people within countries and the reasons due to which this happens.


```{r, echo=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(plotly)
library(DT)

dfperiod_medium = read.csv("Data/WPP2019_Period_Indicators_Medium.csv")
dfm_countries <- dfperiod_medium %>%
  filter(MidPeriod >= 2020) %>%
  filter(Location %in% c("Syrian Arab Republic", "Venezuela (Bolivarian Republic of)", "South Sudan"))

dfperiod_zm = read.csv("Data/WPP2019_Period_Indicators_OtherVariants.csv")
dfzm_countries <- dfperiod_zm %>%
  filter (Variant == "Zero migration") %>%
  filter(Location %in% c("Syrian Arab Republic", "Venezuela (Bolivarian Republic of)", "South Sudan"))
```

*Births in number of births including both sexes combined in thousands (Medium)*
```{r}
plot_birthsmcountries <- ggplot(data=dfm_countries, aes(x=MidPeriod, y=Births, fill=Location, color=Location)) + geom_line()
plot_birthsmcountries
```

This graph displays the total births including both sexes combined in thousands (y-axis) development of South Sudan, the Syrian Arab Republic, and the Bolivarian Republic of Venezuela over time, specifically from 2020 to 2100 (x-axis). It is based on the medium projection variant, which the most popular type because it is based on the median of all trajectories based on a probabilistic model. In general it is interesting to note that Venezuela has the highest birth numbers out of those three countries and this number increases further until around 2030. Afterwards, Venezuela's birth numbers decrease at the fastest rate and it is projected that it will have the lowest birth numbers from 2070 on. Syria seems to have an overall similiar trend with a delay of 20 years compared to Venezuela. However, South Sudan seems to be even further behind of those two countries, as it is projected that its birth numbers are going to increase constantly until 2070 before slowly decreasing.

*Births in number of births including both sexes combined in thousands (Zero migration)*
```{r}
plot_birthszmcountries <- ggplot(data=dfzm_countries, aes(x=MidPeriod, y=Births, fill=Location, color=Location)) + geom_line()
plot_birthszmcountries
```

This graph displays the total births including both sexes combined in thousands (y-axis) development of South Sudan, the Syrian Arab Republic, and the Bolivarian Republic of Venezuela over time, specifically from 2020 to 2100 (x-axis). It is based on the zero migration variant, which assumes that there is no international migration. The curves for South Sudan as well as Venezuela are similiar to the ones based on the medium variant. However, Syria's curve is drastically different as it is projected to have a decreasing amount of births from 2020 on. As mentioned within the Syria-tab a reason could be the return of people, who fled the country during the Syrian war, as Syria was the only country to have a larger population projection with migration than without.

*Deaths in number of deaths including both sexes combined in thousands (Medium)*
```{r}
plot_deathsmcountries <- ggplot(data=dfm_countries, aes(x=MidPeriod, y=Deaths, fill=Location, color=Location)) + geom_line()
plot_deathsmcountries
```

This graph decsribes the total deaths including both sexes combined in thousands (y-axis) development of South Sudan, the Syrian Arab Republic, and the Bolivarian Republic of Venezuela over time, specifically from 2020 to 2100 (x-axis). It is based on the medium projection variant, which the most popular type because it is based on the median of all trajectories based on a probabilistic model. In general Venezuela's curve is concaved and South Sudan's one convexed, which can probably be explained by the birth numbers from the previous graphs. South Sudan's birth numbers are projected to be increasing and eventually surpassing the Venezuela's numbers. Syria's death numbers are increasing until around 2075 before decreasing for around 15 years. Afterwards, the deaths numbers increase once again. The short increase from 2090 to 2100 probably corresponds to the birth numbers from around 2030 to 2050. 

*Deaths in number of deaths including both sexes combined in thousands (Zero migration)*
```{r}
plot_deathszmcountries <- ggplot(data=dfzm_countries, aes(x=MidPeriod, y=Deaths, fill=Location, color=Location)) + geom_line()
plot_deathszmcountries
```

This graph decsribes the total deaths including both sexes combined in thousands (y-axis) development of South Sudan, the Syrian Arab Republic, and the Bolivarian Republic of Venezuela over time, specifically from 2020 to 2100 (x-axis). It is based on the zero migration variant, which assumes that there is no international migration. The curves have similiar shapes as the ones based on the medium variant. Nonetheless, Syria's curve is increasing slower and surpasses South Sudan later and actually is lower again after around 2080.


### Word Cloud and Common Themes in News Coverages
As part of our analysis, we also looked at the most frequent common words that appeared in the article coverages that mentioned migration related terms for each of the top 3 countries of interest. In doing so, we utilized Web article coverages from Factiva database for 2019. The year was chosen to focus on the discussion surrounding the issues of immigrants prior to the COVID pandemic. The overall wordcloud from the corpus of articles is given below. It is followed by the top terms for each country from the set of common terms that existed in separate corpuses by country.




```{r, messages=FALSE, warning=FALSE}
#Input the text files
text <- readLines("Data/all_nations.txt")
text1 <- readLines("Data/syria_v1.txt")
text2 <- readLines("Data/venezuela_v1.txt")
text3 <- readLines("Data/ssudan_v1.txt")
```

```{r}
cloud <- Corpus(VectorSource(text))
cloud1 <- Corpus(VectorSource(text1))
cloud2 <- Corpus(VectorSource(text2))
cloud3 <- Corpus(VectorSource(text3))
```


```{r, warning=FALSE, message=FALSE}
removeNumPunct <- function(x) {
  gsub("[^[:alpha:][:space:]]*", "", x)
}
removeAllCaps <- function(x) {
  gsub("\b[A-Z]+\b", "", x)
}


clean_corpus <- function(corpus) {
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, content_transformer(removeAllCaps))
  corpus <- tm_map(corpus, content_transformer(tolower))
  #adding too common and not insightful words to the stopwords list
  corpus <- tm_map(corpus, removeWords, c("syria","syrian","south","sudan","venezuela","venezuelas","venezuelans","venezuelan","year","years","one","two","three","later","since","month","months","didnt","first","second","third","back","even","now","among","may","get","day","yet","say","country","countries","countrys","president","middle","many","still","says", "bus","left","like","want", "sudanese","sudans","refugee", stopwords("en")))
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, content_transformer(removeNumPunct))
  corpus <- tm_map(corpus, stripWhitespace)
  return(corpus)
}

suc_clean <- clean_corpus(cloud)
suc_tdm <- TermDocumentMatrix(suc_clean)
suc_m <- as.matrix(suc_tdm)
suc_v <- sort(rowSums(suc_m), decreasing = TRUE)
suc_d <- data.frame(word = names(suc_v), freq = suc_v)
```

```{r, message=FALSE, warning=FALSE}
set.seed(1234)
wordcloud(
  words = suc_d$word,
  freq = suc_d$freq,scale = c(2, 0.4),
  min.freq = 5,
  max.words = 100,
  random.order = FALSE,
  rot.per = 0.3,
  colors = brewer.pal(8, "Dark2")
)
```
```{r}
suc_clean1 <- clean_corpus(cloud1)

suc_tdm1 <- TermDocumentMatrix(suc_clean1)

suc_m1 <- as.matrix(suc_tdm1)

suc_v1 <- sort(rowSums(suc_m1), decreasing = TRUE)

suc_d1 <- data.frame(word = names(suc_v1), freq = suc_v1)
```
```{r}
suc_clean2 <- clean_corpus(cloud2)

suc_tdm2 <- TermDocumentMatrix(suc_clean2)

suc_m2 <- as.matrix(suc_tdm2)

suc_v2 <- sort(rowSums(suc_m2), decreasing = TRUE)

suc_d2 <- data.frame(word = names(suc_v2), freq = suc_v2)
```
```{r}
suc_clean3 <- clean_corpus(cloud3)

suc_tdm3 <- TermDocumentMatrix(suc_clean3)

suc_m3 <- as.matrix(suc_tdm3)

suc_v3 <- sort(rowSums(suc_m3), decreasing = TRUE)

suc_d3 <- data.frame(word = names(suc_v3), freq = suc_v3)
```
```{r}
d1_syria <- suc_d1 
names(d1_syria)[names(d1_syria) == "freq"] <- "freq_syria"
d2_venezuela <- suc_d2 
names(d2_venezuela)[names(d2_venezuela) == "freq"] <- "freq_venezuela"
d3_ssudan <- suc_d3 
names(d3_ssudan)[names(d3_ssudan) == "freq"] <- "freq_ssudan"
```


```{r, warning=FALSE, message=FALSE}
#Cleaning up and prepping the dataframe for visualization
#top common words by frequency are in combined3 
Combined2 <- inner_join(d2_venezuela, d3_ssudan, by = "word") 
Combined3<-inner_join(d1_syria, Combined2, by = "word")
```

```{r, warning=FALSE, message=FALSE}
Combined5<- Combined3 %>% 
top_n(5, freq_syria) %>%
  arrange(desc(freq_syria))
```
```{r, warning=FALSE, message=FALSE}
Combined6<- Combined3 %>% 
top_n(5, freq_venezuela) %>%
  arrange(desc(freq_venezuela))
```
```{r, warning=FALSE, message=FALSE}
Combined7<- Combined3 %>% 
top_n(5, freq_ssudan) %>%
  arrange(desc(freq_ssudan))
```


```{r}
#append these multiple dataframes into combined 4
Combined4 <- rbind(Combined5,Combined6, Combined7)
```

```{r, warning=FALSE, message=FALSE}
names(Combined4)[names(Combined4) == "freq_ssudan"] <- "South Sudan"
names(Combined4)[names(Combined4) == "freq_syria"] <- "Syria"
names(Combined4)[names(Combined4) == "freq_venezuela"] <- "Venezuela"
```

```{r, verbose=FALSE}
test1<- reshape2::melt(Combined4, id.vars="word")
names(test1)[names(test1) == "value"] <- "count"
names(test1)[names(test1) == "variable"] <- "Country"
```

```{r}
emotion_dtm <- test1
emotiona_dtm<-emotion_dtm %>%
  group_by(word, Country) 
```
```{r}
emotion_dtm %>% ggplot(aes(x = word, y = count)) +
  geom_col(aes(fill = Country)) +
  facet_wrap(~ Country) +
  coord_flip()+ theme_clean()+
#theme(panel.background = element_rect(fill = "white",
                                        #colour = "black",
                                        #size = 0.5, 
                                        #linetype = "solid"),
        #panel.grid.major.y = element_blank(),
        #panel.grid.major.x = element_line(size = .1, 
                                         # color = "black",
                                          #linetype = "dashed")) 
scale_fill_manual(values = usecol(pal_unikn_pair, n = 3, alpha = 0.8)) +
  labs(x = "Common Words",
       y = "Frequency",
       title = "Frequent Common Words by Country")
```


## Venezuela {.tabset .tabset-fade .tabset-pills}

```{r child='venezuela.Rmd'}
```

## South Sudan {.tabset .tabset-fade .tabset-pills}

```{r child = 'southsudan.Rmd'}
```

## Syria {.tabset .tabset-fade .tabset-pills}

```{r child = 'syria.Rmd'}
```



