---
title: "southsudan"
output: html_document
---

Made up of the 10 southern-most states of Sudan, South Sudan is one of the most diverse countries in Africa. It is home to over 60 different major ethnic groups, and the majority of its people follow traditional religions.

South Sudan gained independence from Sudan on 9 July 2011 as the outcome of a 2005 agreement that ended Africa's longest-running civil war. Independence did not bring conflict in South Sudan to an end. Civil war broke out in 2013 when the president fell out with his then vice president, leading to a conflict that has displaced some 4 million people.

```{r}
library(wbstats)
library(ggplot2)
library(tidyverse)
library(readxl)
```

```{r}
gdp_data <- wb(country = "SSD",
               indicator = c("NY.GDP.PCAP.KD.ZG") , startdate = 2000, enddate = 2017)
gdp_data$date <- as.numeric(gdp_data$date)
```

```{r}
gdp_data %>%
  ggplot(aes(x = factor(date), y = value, group = 1)) + 
  geom_line(group = 1) + ylab("GDP per capita growth") +xlab(NULL) +
  geom_hline(yintercept = 0, color = "red") +
  geom_segment(aes(x = 3.5, xend = 3.5, y = 0, yend = -40), color = "blue", size = 0.2) +
  geom_text(aes(x=3.5, y=-42, label="Gain \n independence"),size=2.5)
  #geom_segment(aes(x = 3.5, xend = 23, y = 0, yend = -7), color = "blue", size = 0.2) +
  #geom_text(aes(x=14.5, y=-8, label="Central Bank\n confirms recession"),size=2.5)
```

```{r}
mig_trend <- read_excel("Data/migration_trends.xlsx", sheet = 2, col_names = TRUE)
```


```{r}

```