---
title: "southsudan"
output: html_document
---


### The Present

Made up of the 10 southern-most states of Sudan, South Sudan is one of the most diverse countries in Africa. It is home to over 60 different major ethnic groups, and the majority of its people follow traditional religions.

South Sudan gained independence from Sudan on 9 July 2011 as the outcome of a 2005 agreement that ended Africa's longest-running civil war. Independence did not bring conflict in South Sudan to an end. Civil war broke out in 2013 when the president fell out with his then vice president, leading to a conflict that has displaced some 4 million people.

```{r}
library(wbstats)
library(ggplot2)
library(tidyverse)
library(readxl)
library(dplyr)
library(leaflet)
```



```{r}
gdp_data_ssu <- wb(country = "SSD",
               indicator = c("NY.GDP.PCAP.KD.ZG") , startdate = 2009, enddate = 2020)
gdp_data_ssu$date <- as.numeric(gdp_data_ssu$date)

pov_data_ssu <- wbstats::wb(country = "SSD", 
                            indicator = "SI.POV.NAHC", startdate = 2009, enddate = 2020, return_wide = TRUE)
pov_data_ssu$date <- pov_data_ssu$date %>%
  as.numeric()

p <- ggplot2::ggplot() +
  ggplot2::geom_bar(data = pov_data_ssu %>%
                      mutate(year = factor(date), `%age population under poverty` = SI.POV.NAHC),
                    aes(x = year, y = `%age population under poverty`, fill = factor(`%age population under poverty`)), stat = "identity") +
  ggplot2::geom_line(data = gdp_data_ssu %>%
                       mutate(year = factor(date)), aes(x = year, y = value, group = 1, color = "GDP Growth Rate")) +
  xlab(NULL) + ylab(NULL)  +
  scale_fill_viridis(discrete=TRUE, guide=FALSE, option="A", direction = -1) + theme(legend.position = "none")

ggplotly(p)%>%
  plotly::layout(title = list(text = paste0('People living below poverty line & GDP per capita growth (2009-16)'                                  )))


#+ ylab("GDP per capita growth")
  


```
There is a clear connection between decrease in GDP Growth rates and the increasing number of people living below the national poverty lines. Year 2016, more than 80% of the population of the country was living below the national poverty line. The international poverty line, which is currently \$1.90 a day, is the threshold that determines whether someone is living in poverty. The estimates in South Sudan are based on national poverty lines which will be at the most similar or lesser than the international poverty line at $1.90 a day.

```{r}
gdp_data_ssu <- wbstats::wb(country = "SSD",
               indicator = c("NY.GDP.PCAP.KD.ZG") , startdate = 2000, enddate = 2017)
gdp_data_ssu$date <- as.numeric(gdp_data_ssu$date)
```

```{r, warning=FALSE, message=FALSE}
# Importing migrant origin and destination numbers for South Sudan
destination_data <- readxl::read_excel("Data/UN_MigrantStockByOriginAndDestination_2019.xlsx", sheet = 2, skip = 15, col_names = TRUE, trim_ws = TRUE)

# Subsetting origin to South Sudan
destination_data_ssu <- destination_data %>%
  dplyr::filter(...3 == "South Sudan")

destination_data_ssu$Total <- destination_data_ssu$Total %>%
  as.numeric()

# Subsetting origin to Syria and also 2018. This will be used in the map.
destination_data_ssu_2019 <- destination_data_ssu %>%
  dplyr::filter(...1 == 2019)

# I am not interested in the first 9 columns. Only keeping columns which have data about the destination countries
destination_data_ssu_2019 <- destination_data_ssu_2019[c(10:241)]

# Making the table vertical- gather
destination_data_ssu_2019 <- tidyr::gather(destination_data_ssu_2019, key = "country", value = "value")

destination_data_ssu_2019$value <- destination_data_ssu_2019$value %>%
  as.numeric()
```


Let us see what the migration trends in the country have been.
```{r, warning=FALSE}

destination_data_ssu %>%
  # Removing rows without data
  filter(...1 >= 2010) %>%
  mutate(year = factor(...1)) %>%
  ggplot() +
  geom_point(aes(x = year, y = Total, color = "red")) +
  geom_line(aes(x = year, y = Total, group = 1, color = "red")) +
  ylab(NULL) + xlab(NULL) +
  geom_segment(aes(x = 1.2, xend = 1.2, y = 0, yend = 381000), color = "orange", size = 0.2) +
  geom_label(aes(x = 1.2, y = 200000, label = "2011:\n South Sudan\nis born", fill = "yellow"), size = 2.5) +
  geom_segment(aes(x = 1.6, xend = 1.6, y = 0, yend = 602000), color = "orange", size = 0.2) +
  geom_label(aes(x=1.6, y=200000, label="2013:\nCivil War\nerupts", fill = "yellow"),size=2.5) +
  geom_segment(aes(x = 2.2, xend = 2.2, y = 0, yend = 855000), color = "orange", size = 0.2) +
  geom_label(aes(x=2.2, y=200000, label="2016:\nUN claims ethnic\n cleansing in S. Sudan", fill = "yellow"),size=2.5) +
  labs(
    title = "Evolution of migration",
    subtitle = "2010 - 2019",
    caption = "source: World Bank, Global Poverty Working Group."
  ) +
  theme(
    legend.position = "none"
  ) +
  scale_color_viridis(discrete=TRUE, guide=FALSE, option="D", direction = 1)

```

The GDP growth rate declined rapidly in 2010 and the same period saw an almost exponential growth in the number of migrants leaving the country. Since 2010, the country has seen continous periods of civil unrest. The number of migrants seem to have plateaued after reaching just around 850,000 people per year.

Now we can see where have the migrants landed after leaving their home country. A very large number of migrants from South Sudan are refugees and asylum seekers who have moved to other countries to search for a safe haven.

This map shows the destinations of the refugees and asylum seekers from South Sudan in the year 2019.
```{r}
# importing the country centroid data
world <- rgdal::readOGR("Data/country_centroids_az8/country_centroids_az8.shp", verbose = FALSE)

world_sub <- world@data %>%
  dplyr::filter(world@data$type != "Dependency")

# Merging data with shape file
world_ssu <- merge(world_sub, destination_data_ssu_2019, by.x = "sovereignt", by.y = "country", all.x = TRUE)

world_ssu_ssu <- world_ssu %>%
  dplyr::filter(sovereignt == "South Sudan")

group <- c()
lng <- c()
lat <- c()
groupval = 1

for(i in 1:nrow(world_ssu)){
  # If there is a connection between destination and origin country
  if(!is.na(world_ssu$value[i])){
    # Enter origin country first
    group <- c(group, groupval)
    lat <- c(lat, world_ssu_ssu$Latitude)
    lng <- c(lng, world_ssu_ssu$Longitude)
    
    # Enter destination country for same groupvalue
    group <- c(group, groupval)
    lat <- c(lat, world_ssu$Latitude[i])
    lng <- c(lng, world_ssu$Longitude[i])
    
    # Increment group val
    groupval = groupval + 1
  }
}

df <- data.frame(group=group, lng=lng, lat=lat)

pal <- colorNumeric("Blues", df$group)

content <- sprintf("<strong>%s</strong><br/>%g",
                  world_ssu$sovereignt,
                  world_ssu$value) %>% lapply(htmltools::HTML)

###### Flow graph
destination_data_ssu <- destination_data_ssu[c(1, 10:241)]

# Rename column
destination_data_ssu <- rename(destination_data_ssu, c("year" = "...1"))
flow_data <- destination_data_ssu %>%
  pivot_longer(-year, names_to = "country", values_to = "count")

world_sub1 <- world_sub %>%
  dplyr::select(sovereignt, Latitude, Longitude)
world_sub1 <- rename(world_sub1, c("lat1" = "Latitude", "lng1" = "Longitude"))

flow_data <- merge(flow_data, world_sub1, by.x = "country", by.y = "sovereignt")
flow_data$lat0 = world_ssu_ssu$Latitude
flow_data$lng0 = world_ssu_ssu$Longitude
flow_data$count <- as.numeric(flow_data$count)
flow_data <- drop_na(flow_data)

binpal <- colorBin("-RdYlBu", world_ssu$value, 6, pretty = FALSE)

leaflet(flow_data) %>%
  setView(lat = 7.308779, lng = 30.2479, zoom = 4) %>%
  addTiles('https://tiles.stadiamaps.com/tiles/osm_bright/{z}/{x}/{y}{r}.png', options = providerTileOptions(minZoom = 2, maxZoom = 5)) %>%
  addFlows(
    flow_data$lng0, flow_data$lat0, flow_data$lng1, flow_data$lat1,
    flow = flow_data$count,
    time = flow_data$year,
    color = "red",
    opacity = 0.5,
    dir = 1,
    popup = popupArgs(labels = "# of Emigrants"),
    initialTime = 2019,
    minThickness = 0.2,
    maxThickness = 10
  ) %>%
  addMinicharts(
    lat = flow_data$lat1,
    lng = flow_data$lng1,
  chartdata = flow_data$count,
  time = flow_data$year,
  maxValues = NULL,
  type = "polar-area",
  fillColor = "blue",
  colorPalette = ~binpal(flow_data$count),
  width = 40,
  height = 40,
  opacity = 0.7,
  showLabels = TRUE,
  labelMinSize = 8,
  labelMaxSize = 24,
  transitionTime = 750,
  popup = popupArgs(labels = "# of Emigrants"),
  legendPosition = "topright",
  initialTime = 2019
)

# leaflet::leaflet() %>%
#   setView(6.8770, 31.34165036, zoom = 4) %>%
#   addTiles(options = providerTileOptions(minZoom = 3, maxZoom = 5)) %>%
#   addCircles(data = world_ssu,
#              lat = world_ssu$Latitude,
#              lng = world_ssu$Longitude,
#              radius = world_ssu$value,
#              fillColor = world_ssu$value,
#              opacity = 0.8, fillOpacity = 0.7,
#              popup = content, label = content, labelOptions(
#                     style = list("font-weight" = "normal", padding = "3px 8px"),
#                     textsize = "15px",
#                     direction = "auto")) %>%
#   addPolylines(data = df,
#                lng = df$lng,
#                lat = df$lat,
#                group = df$group,
#                color = pal(df$group),
#                opacity = 0.3,
#                weight = 1)

```

Migrants from South Sudan have migrated majorly to African countries and a few to India in the Asian sub-continent. It seems that South Sudan migrants might be either financially drained to make long distance journeys to US/ Canada/ Europe which are popular destinations for migrants all over the world or it seems that South Sudanese people are not being openly accepted in these countries.

Given that for more than 10 years more than 50% of the population has been living below the poverty line hypothesis 1- makes more sense. Also, analysing the word clouds of articles on South Sudan migration seem to highlight the humanitarian crisis this war has taken.

Word-Cloud for Article Coverages: South Sudan

Now, let's look at the frequent terms that come up in articles that mentioned migration related terms and South Sudan. In doing so, we utilized Web article coverages from Factiva database for 2019 and selected the recent 20 articles pertaining to South Sudan that also mentioned migration related terms such as immigrants, migration, refugee, migrant and asylum seekers. The year was chosen to focus on the discussion surrounding the issues of immigrants prior to the COVID pandemic. 

We can infer that the discussion revolves around internal conflict in South Sudan that has displaced many people. South Sudan gained independence from Sudan in July 2011, but the ruling political party that originally led the way for independence, is divided and fighting for power which erupted into violence in the streets of the capital, Juba. South Sudan is one of the most fled countries in the world, alongside Syria, Afghanistan and Venezuela.
```{r, message=FALSE, warning=FALSE, verbose=FALSE}
library(ggplot2)
library(dplyr)
library(stringi)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(corpus)
library(purrr)
library(gower)
library(lme4)
library(multcomp)
library(mvtnorm)
library(corpustools)
```

```{r, message=FALSE, warning=FALSE, verbose=FALSE}
text3 <- readLines("Data/ssudan_v1.txt")
cloud3 <- Corpus(VectorSource(text3))
```

```{r, message=FALSE, warning=FALSE, verbose=FALSE}
removeNumPunct <- function(x) {
  gsub("[^[:alpha:][:space:]]*", "", x)
}
removeAllCaps <- function(x) {
  gsub("\b[A-Z]+\b", "", x)
}


clean_corpus <- function(corpus) {
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, content_transformer(removeAllCaps))
  corpus <- tm_map(corpus, content_transformer(tolower))
  #adding too common and not insightful words to the stopwords list
  corpus <- tm_map(corpus, removeWords, c("syria","syrian","south","sudan","venezuela","venezuelas","venezuelans","venezuelan","year","years","one","two","three","later","since","month","months","didnt","first","second","third","back","even","now","among","may","get","day","yet","say","country","countries","countrys","president","middle","many","still","says", "bus","left","like","want", "sudanese","sudans","refugee", stopwords("en")))
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, content_transformer(removeNumPunct))
  corpus <- tm_map(corpus, stripWhitespace)
  return(corpus)
}
```

```{r, message=FALSE, warning=FALSE, verbose=FALSE}
suc_clean3 <- clean_corpus(cloud3)

suc_tdm3 <- TermDocumentMatrix(suc_clean3)

suc_m3 <- as.matrix(suc_tdm3)

suc_v3 <- sort(rowSums(suc_m3), decreasing = TRUE)

suc_d3 <- data.frame(word = names(suc_v3), freq = suc_v3)
```
```{r, message=FALSE, warning=FALSE, verbose=FALSE}
set.seed(1234)
wordcloud(
  words = suc_d3$word,
  freq = suc_d3$freq,scale = c(2, 0.4),
  min.freq = 5,
  max.words = 100,
  random.order = FALSE,
  rot.per = 0.3,
  colors = brewer.pal(8, "Dark2")
)
```



### The Future
```{r, echo=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(plotly)
library(DT)

dfpop = read.csv("Data/WPP2019_TotalPopulationBySex.csv")
```

*Population development in South Sudan (Medium vs. zero-migration)*
```{r}
dfpop_sudan <- dfpop %>%
  filter(Variant %in% c("Medium", "Zero migration")) %>%
  filter(Location == "South Sudan")
plot_popsudan <- ggplot(data=dfpop_sudan, aes(x=Time, y=PopTotal, fill=Variant, color=Variant)) + geom_line()
plot_popsudan
```

This graph illustrates the total population (y-axis) development of South Sudan over time (x-axis). In the period from 1950 to 2019 the population is increasing almost constantly with the exception from around 1985 to 19959 as well as 2015 to 2019. South Sudan has a history of having issues with their census, which might be a reason for the two 'bumps' in the generally increasing curve. From 2020 to 2100 the graph includes two different curves. The red one is the medium projection variant, which the most popular type because it is based on the median of all trajectories based on a probabilistic model. The blue line describes the zero migration variant, which assumes that there is no international migration and projects the population based on that. Overall it seems like people tend to leave the country or at least there could be more people leaving the country than people coming in.  

