---
title: "syria"
output: html_document
---

### The Present

After Syria gained its independence in 1946, political life in the country was highly unstable, owing in large measure to intense friction between the country’s social, religious, and political groups. In 1970 Syria came under the authoritarian rule of Pres. Hafiz al-Assad. After Assad’s death in 2000, his son Bashar al-Assad became president. Bashar al-Assad ultimately continued his father’s authoritarian style of governments to quash political dissent. Long-suppressed internal tensions led to the outbreak of the Syrian Civil War in 2011.

```{r}
library(wbstats)
library(ggplot2)
library(tidyverse)
library(lubridate)
library(ggthemes)
library(viridis)
library(plotly)
library(RColorBrewer)
library(leaflet)
library(leaflet.minicharts)
```

```{r}
gdp_data_syr <- wbstats::wb(country = "SYR",
               indicator = c("NY.GDP.PCAP.KD.ZG") , startdate = 2000, enddate = 2017)
gdp_data_syr$date <- as.numeric(gdp_data_syr$date)
```

```{r}
p <- gdp_data_syr %>%
  mutate(year = factor(date)) %>%
  ggplot(aes(x = year, y = value, group = 1)) + 
  geom_line(group = 1) + ylab("GDP per capita growth") +xlab(NULL) +
  geom_hline(yintercept = 0, color = "red")

ggplotly(p) %>%
  plotly::layout(title = list(text = paste0('GDP per capita growth (2000-7)')))
```


```{r, warning=FALSE, message=FALSE}
# Importing migrant origin and destination numbers for Syria
destination_data <- readxl::read_excel("Data/UN_MigrantStockByOriginAndDestination_2019.xlsx", sheet = 2, skip = 15, col_names = TRUE, trim_ws = TRUE)

# Subsetting origin to Syria
destination_data_syr <- destination_data %>%
  dplyr::filter(...3 == "Syrian Arab Republic")

destination_data_syr$Total <- destination_data_syr$Total %>%
  as.numeric()

# Subsetting origin to Syria and also 2018. This will be used in the map.
destination_data_syr_2019 <- destination_data_syr %>%
  dplyr::filter(...1 == 2019)

# I am not interested in the first 9 columns. Only keeping columns which have data about the destination countries
destination_data_syr_2019 <- destination_data_syr_2019[c(10:241)]

# Making the table vertical- gather
destination_data_syr_2019 <- tidyr::gather(destination_data_syr_2019, key = "country", value = "value")

destination_data_syr_2019$value <- destination_data_syr_2019$value %>%
  as.numeric()
```

A severe decline in the GDP growth rate in 2004 onwards led to a sharp increase in the number of migrants. 

```{r}

destination_data_syr %>%
  mutate(year = factor(...1)) %>%
  ggplot() +
  geom_point(aes(x = year, y = Total)) +
  geom_line(aes(x = year, y = Total, group = 1)) +
  ylab(NULL) + xlab(NULL) +
  geom_segment(aes(x = 3, xend = 3, y = 0, yend = 834916), color = "orange", size = 0.2) +
  geom_label(aes(x = 3, y = 200000, label = "2000:\n Bashar Assad\ncomes to power", fill = "yellow"), size = 2.5) +
  geom_segment(aes(x = 3.8, xend = 3.8, y = 0, yend = 851000), color = "orange", size = 0.2) +
  geom_label(aes(x = 3.8, y = 500000, label = "2004:\n US imposes\nsanctions", fill = "yellow"), size = 2.5) +
  geom_segment(aes(x = 5.2, xend = 5.2, y = 0, yend = 1600000), color = "orange", size = 0.2) +
  geom_label(aes(x = 5.2, y = 1000000, label = "2011:\n Arab Spring\nSyrian Civil War begins", fill = "yellow"), size = 2.5) +
  geom_segment(aes(x = 5.5, xend = 5.5, y = 0, yend = 1300000), color = "orange", size = 0.2) +
  geom_label(aes(x=5.5, y=500000, label="2012:\nUN declares state of\ncivil war in Syria", fill = "yellow"),size=2.5) +
  geom_segment(aes(x = 6.8, xend = 6.8, y = 0, yend = 867848), color = "orange", size = 0.2) +
  geom_label(aes(x=6.8, y=200000, label="2018:\nUS-led missile\nstrikes", fill = "yellow"),size=2.5) +
  labs(
    title = "Evolution of migration",
    subtitle = "1990 - 2019",
    caption = "source: World Bank, Global Poverty Working Group."
  ) +
  theme(
    legend.position = "none"
  ) +
  scale_color_viridis(discrete=TRUE, guide=FALSE, option="D", direction = 1)

```

After experiencing a mass exodus in 2010 when more than 1.5 million people emigrated from the country there has been some decline but the number of migrants still hovers close to less than a million. In the year 2010 almost 1.1 million people moved to neighbouring country Iraq.

Similar to trend observed in South Sudan, Syrian migrants have not travelled to far off countries in the American and the European continents. They have limited themselves to the North-east African countries or western Asia.

This map shows the destinations of the refugees and asylum seekers from Syria in the year 2019.

```{r, eval=FALSE}
# world_syr %>%
#   group_by(sovereignt) %>%
#   summarise(count = n()) %>%
#   arrange(desc(count))
# 
# world_syr %>%
#   filter(sovereignt == "United Kingdom")
# 
# world_syr %>%
#   filter(sovereignt == "Australia")
# 
# world_syr %>%
#   filter(sovereignt == "France")
```

```{r, verbose=FALSE}
#importing the country centroid data
world <- rgdal::readOGR("Data/country_centroids_az8/country_centroids_az8.shp", verbose = FALSE)

world_sub <- world@data %>%
  dplyr::filter(world@data$type != "Dependency")

# Merging data with shape file
world_syr <- merge(world_sub, destination_data_syr_2019, by.x = "sovereignt", by.y = "country", all.x = TRUE)

world_syr_syr <- world_syr %>%
  dplyr::filter(sovereignt == "Syria")

group <- c()
lng <- c()
lat <- c()
groupval = 1

for(i in 1:nrow(world_syr)){
  # If there is a connection between destination and origin country
  if(!is.na(world_syr$value[i])){
    # Enter origin country first
    group <- c(group, groupval)
    lat <- c(lat, world_syr_syr$Latitude)
    lng <- c(lng, world_syr_syr$Longitude)
    
    # Enter destination country for same groupvalue
    group <- c(group, groupval)
    lat <- c(lat, world_syr$Latitude[i])
    lng <- c(lng, world_syr$Longitude[i])
    
    # Increment group val
    groupval = groupval + 1
  }
}

df_syr <- data.frame(group=group, lng=lng, lat=lat)

pal <- colorNumeric("Blues", df_syr$group)

content <- sprintf("<strong>%s</strong><br/>%g",
                  world_syr$sovereignt,
                  world_syr$value) %>% lapply(htmltools::HTML)

###### Flow graph
destination_data_syr <- destination_data_syr[c(1, 10:241)]

# Rename column
destination_data_syr <- dplyr::rename(destination_data_syr, c("year" = "...1"))
flow_data <- destination_data_syr %>%
  pivot_longer(-year, names_to = "country", values_to = "count")

world_sub1 <- world_sub %>%
  dplyr::select(sovereignt, Latitude, Longitude)
world_sub1 <- dplyr::rename(world_sub1, c("lat1" = "Latitude", "lng1" = "Longitude"))

flow_data <- merge(flow_data, world_sub1, by.x = "country", by.y = "sovereignt")
flow_data$lat0 = world_syr_syr$Latitude
flow_data$lng0 = world_syr_syr$Longitude
flow_data$count <- as.numeric(flow_data$count)
flow_data <- drop_na(flow_data)

binpal <- colorBin("-RdYlBu", world_syr$value, 6, pretty = FALSE)

leaflet(flow_data, options = leafletOptions(zoomControl = TRUE, minZoom = 3, maxZoom = 6)) %>%
    addProviderTiles(providers$CartoDB.Positron)%>%
    setView(lat = 35.02547	, lng = 38.50788, zoom = 5) %>%
  addFlows(
    flow_data$lng0, flow_data$lat0, flow_data$lng1, flow_data$lat1,
    flow = flow_data$count,
    time = flow_data$year,
    color = "red",
    opacity = 0.5,
    dir = 1,
    popup = popupArgs(labels = "# of Emigrants"),
    initialTime = 2019,
    minThickness = 0.2,
    maxThickness = 10
  ) %>%
  addMinicharts(
    lat = flow_data$lat1,
    lng = flow_data$lng1,
  chartdata = flow_data$count,
  time = flow_data$year,
  maxValues = NULL,
  type = "polar-area",
  fillColor = "blue",
  colorPalette = ~binpal(flow_data$count),
  width = 40,
  height = 40,
  opacity = 0.7,
  showLabels = TRUE,
  labelMinSize = 6,
  labelMaxSize = 24,
  transitionTime = 750,
  popup = popupArgs(labels = "# of Emigrants"),
  legendPosition = "topright",
  initialTime = 2019
)

# leaflet::leaflet() %>%
#   setView(lng = 38.50788, lat = 35.02547, zoom = 2) %>%
#   addTiles(options = providerTileOptions(minZoom = 2, maxZoom = 5)) %>%
#   addCircles(data = world_syr,
#              lat = world_syr$Latitude,
#              lng = world_syr$Longitude,
#              radius = world_syr$value,
#              fillColor = world_syr$value,
#              opacity = 0.8, fillOpacity = 0.7,
#              popup = content, label = content, labelOptions(
#                     style = list("font-weight" = "normal", padding = "3px 8px"),
#                     textsize = "15px",
#                     direction = "auto")) %>%
#   addPolylines(data = df_syr,
#                lng = df_syr$lng,
#                lat = df_syr$lat,
#                group = df_syr$group,
#                color = pal(df_syr$group),
#                opacity = 0.1,
#                weight = 1,
#                fillOpacity = df_syr$group,
#                fillColor = pal(df_syr$group))
#   

```

The graph below represents the number of deaths that have taken place due to Syrian Civil War since 2011.

```{r}
# Loading casuality data
cas_syr <- read.csv("Data/VDC_Syria_CASREP.csv", stringsAsFactors = FALSE)

# converting date into year
cas_syr$deathdate <- cas_syr$deathdate %>%
  lubridate::as_date() %>%
  lubridate::year()

# Aggregating the data, Selecting only civilians
cas_syr1 <- cas_syr %>%
  filter(status == "Civilian") %>%
  group_by(deathdate) %>%
  summarise(count = n())

p <- cas_syr1 %>%
  arrange(deathdate) %>%
  mutate(year = factor(deathdate)) %>%
  ggplot(aes(x=year, y=count, size=count, fill=factor(count))) +
    geom_point(alpha=0.5, shape=21, color="black") +
    scale_fill_viridis(discrete=TRUE, guide=FALSE, option="A") +
    theme(legend.position="none") +
    ylab("Deaths") +
    xlab(NULL)

ggplotly(p) %>%
  plotly::layout(title = list(text = paste0('Civilian deaths due to the war (2011-2019)',
                                    '<br>',
                                    '<sup>',
                                    'source: Casualty Reports from the Violations Documentation Center in Syria.',
                                    '</sup>')))
```
This table sheds more light on how many of the victims of this war have been children and civilian adults. 
```{r}
cas_syr %>%
  dplyr::select(status, gender, deathdate) %>%
  dplyr::group_by(deathdate, status, gender) %>%
  dplyr::summarise(count = n()) %>%
  dplyr::arrange(deathdate, gender) %>%
  DT::datatable()
```

Word-Cloud for Article Coverages: Syria

```{r, message=FALSE, warning=FALSE, verbose=FALSE}
library(ggplot2)
library(dplyr)
library(stringi)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(corpus)
library(purrr)
library(gower)
library(lme4)
library(multcomp)
library(mvtnorm)
library(corpustools)
```

```{r, message=FALSE, warning=FALSE, verbose=FALSE}
text1 <- readLines("Data/syria_v1.txt")
cloud1 <- Corpus(VectorSource(text1))
```


```{r, message=FALSE, warning=FALSE, verbose=FALSE}
removeNumPunct <- function(x) {
  gsub("[^[:alpha:][:space:]]*", "", x)
}
removeAllCaps <- function(x) {
  gsub("\b[A-Z]+\b", "", x)
}


clean_corpus <- function(corpus) {
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, content_transformer(removeAllCaps))
  corpus <- tm_map(corpus, content_transformer(tolower))
  #adding too common and not insightful words to the stopwords list
  corpus <- tm_map(corpus, removeWords, c("syria","syrian","south","sudan","venezuela","venezuelas","venezuelans","venezuelan","year","years","one","two","three","later","since","month","months","didnt","first","second","third","back","even","now","among","may","get","day","yet","say","country","countries","countrys","president","middle","many","still","says", "bus","left","like","want", "sudanese","sudans","refugee", stopwords("en")))
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, content_transformer(removeNumPunct))
  corpus <- tm_map(corpus, stripWhitespace)
  return(corpus)
}

suc_clean1 <- clean_corpus(cloud1)

suc_tdm1 <- TermDocumentMatrix(suc_clean1)

suc_m1 <- as.matrix(suc_tdm1)

suc_v1 <- sort(rowSums(suc_m1), decreasing = TRUE)

suc_d1 <- data.frame(word = names(suc_v1), freq = suc_v1)
```

Now, let's look at the frequent terms that come up in articles that mentioned migration related term and Syria. In doing so, we utilized Web article coverages from Factiva database for 2019 and selected the recent 20 articles pertaining to Syria that also mentioned migration related terms such as immigrants, migration, refugee, migrant and asylum seekers. The year was chosen to focus on the discussion surrounding the issues of immigrants prior to the COVID pandemic. 

We can see that Turkey comes up a lot in discussions pertaining to Syria followed by Russia, United States.Turkey has been diplomatically and militarily involved in the Syrian Civil War since its outbreak in 2011. In 2017, Turkish forces launched an operation to establish observation posts in the northern Idlib Governorate, in coordination with Russia. On the other hand, the United States has sought to reduce its involvement in Syria and does not back the Bashar Al Ashad led government while Russia supports Ashad.
```{r, message=FALSE, warning=FALSE, verbose=FALSE}
set.seed(1234)
wordcloud(
  words = suc_d1$word,
  freq = suc_d1$freq,scale = c(2, 0.4),
  min.freq = 5,
  max.words = 100,
  random.order = FALSE,
  rot.per = 0.3,
  colors = brewer.pal(8, "Dark2")
)
```

### The Future
```{r, echo=FALSE, warning=FALSE, message=FALSE}
dfpop = read.csv("Data/WPP2019_TotalPopulationBySex.csv")
```

*Population development in Syria (Medium vs. zero-migration)*
```{r}
dfpop_syria <- dfpop %>%
  filter(Variant %in% c("Medium", "Zero migration")) %>%
  filter(Location == "Syrian Arab Republic") %>%
  filter(Time <= "2020")
dfpop_syria2 <- dfpop %>%
  filter(Variant %in% c("Medium", "Zero migration")) %>%
  filter(Location == "Syrian Arab Republic") %>%
  filter(Time >= "2020")
plot_popsyria <- ggplot() + geom_line(data=dfpop_syria, aes(x=Time, y=PopTotal, fill=Variant, color=Variant)) + geom_point(size=0.1, data=dfpop_syria2, aes(x=Time, y=PopTotal, fill=Variant, color=Variant))
ggplotly(plot_popsyria)
```

This graph illustrates the total population (y-axis) development of the Syrian Arab Republic over time (x-axis). In the period from 1950 to 2019 the population is increasing constantly with the exception from around 2015 to 2019. A possible reason for the development during that period is the Syrian war. From 2020 to 2100 the graph includes two different curves. The red one is the medium projection variant, which the most popular type because it is based on the median of all trajectories based on a probabilistic model. The blue line describes the zero migration variant, which assumes that there is no international migration and projects the population based on that. Interestingly, the population increases at a faster rate when there is migration. That is suprising for a country that experienced a decrease in the total population due to war. However, a possible explanation could be the return of Syrians who fled and registered as refugees in other countries. 