
Venezuela is a country located at the northern end of South America. It occupies a roughly triangular area that is larger than the combined areas of France and Germany.

The economy of Venezuela is a market-based mixed economy based largely on the petroleum and manufacturing sectors, and has been in a state of total economic collapse since the mid-2010s. This has aled to a mass-exodus of people from the country which has been facing an economic and political turmoil since a long time.

```{r}
library(wbstats)
library(ggplot2)
```

```{r}
gdp_data_ven <- wb(country = "VEN",
               indicator = c("NY.GDP.PCAP.KD.ZG") , startdate = 2000, enddate = 2017)
gdp_data_ven$date <- as.numeric(gdp_data_ven$date)
```

```{r}
gdp_data_ven %>%
  ggplot(aes(x = factor(date), y = value, group = 1)) + 
  geom_line(group = 1) + ylab("GDP per capita growth") +xlab(NULL) +
  geom_hline(yintercept = 0, color = "red")
```

The GDP per capita growth has been dipping since reaching its peak in 2004.

Let us see what the migration trends of the country has been.
```{r}
# mig_ven <- wbstats::wb(country = "VEN",indicator = c("SM.POP.NETM"),  startdate = "2000", enddate = "2020", return_wide = TRUE)
# mig_ven$date <- as.numeric(mig_ven$date)
```

```{r}
# ggplot(mig_ven) +
#   geom_line(aes(x = factor(date), y = SM.POP.NETM, group = 1)) +
#   xlab(NULL) + ylab(NULL)
```

```{r}
# tmap_mode("view")
# tm_shape(World) +
#     tm_polygons(c("HPI", "economy")) +
#     tm_facets(sync = TRUE, ncol = 2)
```



```{r, warning=FALSE, message=FALSE}
# Importing migrant origin and destination numbers for venezuela
destination_data <- readxl::read_excel("Data/UN_MigrantStockByOriginAndDestination_2019.xlsx", sheet = 2, skip = 15, col_names = TRUE, trim_ws = TRUE)

# Subsetting origin to Venezuela
destination_data_ven <- destination_data %>%
  dplyr::filter(...3 == "Venezuela (Bolivarian Republic of)")

destination_data_ven$Total <- destination_data_ven$Total %>%
  as.numeric()

# Subsetting origin to Venezuela and also 2018. This will be used in the map.
destination_data_ven_2019 <- destination_data_ven %>%
  dplyr::filter(...1 == 2019)

# I am not interested in the first 9 columns. Only keeping columns which have data about the destination countries
destination_data_ven_2019 <- destination_data_ven_2019[c(10:241)]

# Making the table vertical- gather
destination_data_ven_2019 <- tidyr::gather(destination_data_ven_2019, key = "country", value = "value")

destination_data_ven_2019$value <- destination_data_ven_2019$value %>%
  as.numeric()
```

```{r}
options(scipen = 999)

destination_data_ven %>%
  ggplot() +
  geom_point(aes(x = factor(...1), y = Total)) +
  geom_line(aes(x = factor(...1), y = Total, group = 1)) +
  ylab(NULL) + xlab(NULL) + 
  geom_segment(aes(x = 1.1, xend = 1.1, y = 0, yend = 1000000), color = "blue", size = 0.2) +
  geom_label(aes(x = 1.1, y = 800000, label = "1992:\n Venezuela is\n3rd richest country"), size = 2.5) +
  geom_segment(aes(x = 2.9, xend = 2.9, y = 0, yend = 1000000), color = "blue", size = 0.2) +
  geom_label(aes(x = 2.9, y = 800000, label = "1999:\n Chavez begins\nfirst term"), size = 2.5) +
  geom_segment(aes(x = 3.3, xend = 3.3, y = 0, yend = 1000000), color = "blue", size = 0.2) +
  geom_label(aes(x = 3.3, y = 600000, label = "2002:\n Armed forces\nrebel"), size = 2.5) +
  geom_segment(aes(x = 5.5, xend = 5.5, y = 0, yend = 1400000), color = "blue", size = 0.2) +
  geom_label(aes(x=5.5, y=1300000, label="2013:\nPresident Chavez dies.\nMaduro elected"),size=2.5) +
  geom_segment(aes(x = 5.8, xend = 5.8, y = 0, yend = 1400000), color = "blue", size = 0.2) +
  geom_label(aes(x=6, y=1100000, label="2014:\nCentral Bank\n confirms recession"),size=2.5)
```



```{r, message=FALSE}
world <- rgdal::readOGR("Data/country_centroids_az8/country_centroids_az8.shp")

world_ven <- merge(world, destination_data_ven_2019, by.x = "sovereignt", by.y = "country", all.x = TRUE)

world_ven_ven <- world_ven@data %>%
  filter(sovereignt == "Venezuela")

content <- sprintf("<strong>%s</strong><br/>%g",
                  world_ven$sovereignt,
                  world_ven$value) %>% lapply(htmltools::HTML)

group <- c()
lng <- c()
lat <- c()
groupval = 1

for(i in 1:nrow(world_ven)){
  # If there is a connection between destination and origin country
  if(!is.na(world_ven$value[i])){
    # Enter origin country first
    group <- c(group, groupval)
    lat <- c(lat, world_ven_ven$Latitude)
    lng <- c(lng, world_ven_ven$Longitude)
    
    # Enter destination country for same groupvalue
    group <- c(group, groupval)
    lat <- c(lat, world_ven$Latitude[i])
    lng <- c(lng, world_ven$Longitude[i])
    
    # Increment group val
    groupval = groupval + 1
  }
}

df_ven <- data.frame(group=group, lng=lng, lat=lat)

pal <- colorNumeric("Blues", df_ven$group)

leaflet::leaflet() %>%
  setView(-66.1818412311, 7.12422421273, zoom = 2) %>%
  addTiles(options = providerTileOptions(minZoom = 2, maxZoom = 5)) %>%
  addCircles(data = world_ven,
             lat = world_ven$Latitude,
             lng = world_ven$Longitude,
             radius = world_ven$value,
             fillColor = world_ven$value,
             opacity = 0.8, fillOpacity = 0.7,
             popup = content, label = content, labelOptions(
                    style = list("font-weight" = "normal", padding = "3px 8px"),
                    textsize = "15px",
                    direction = "auto")) %>%
  addPolylines(data = df_ven,
               lng = df_ven$lng,
               lat = df_ven$lat,
               group = df_ven$group,
               color = pal(df_ven$group),
               opacity = 0.1,
               weight = 1,
               fillOpacity = df_ven$group,
               fillColor = pal(df_ven$group))
  
  
```