


Venezuela is a country located at the northern end of South America. It occupies a roughly triangular area that is larger than the combined areas of France and Germany.

The economy of Venezuela is a market-based mixed economy based largely on the petroleum and manufacturing sectors, and has been in a state of total economic collapse since the mid-2010s. This has aled to a mass-exodus of people from the country which has been facing an economic and political turmoil since a long time.

```{r}
library(wbstats)
library(ggplot2)
```

```{r}
gdp_data <- wb(country = "VEN",
               indicator = c("NY.GDP.PCAP.KD.ZG") , startdate = 2000, enddate = 2017)
gdp_data$date <- as.numeric(gdp_data$date)
```

```{r}
gdp_data %>%
  ggplot(aes(x = factor(date), y = value, group = 1)) + 
  geom_line(group = 1) + ylab("GDP per capita growth") +xlab(NULL) +
  geom_hline(yintercept = 0, color = "red") +
  geom_segment(aes(x = 14.1, xend = 14.1, y = 0, yend = 10), color = "blue", size = 0.2) +
  geom_text(aes(x=14.2, y=10, label="President Chavez dies."),size=2.5) +
  geom_segment(aes(x = 15, xend = 15, y = 0, yend = -7), color = "blue", size = 0.2) +
  geom_text(aes(x=14.5, y=-8, label="Central Bank\n confirms recession"),size=2.5)
```

The GDP per capita growth has been dipping since reaching its peak in 2004.

```{r}

```